---
title: "AHA2019 -- Graphics I"
output: html_notebook
---

# Title: "Graphics with Baptism Records"
# Name:

# Load required functions and packages
library(ggplot2)
library(readr)
library(dplyr)

theme_set(theme_minimal())

The first step in this lab is to read in the Arbuthnot dataset, an
historically important set of records from late 17th century baptism
records. To do this, run the following line of code:

```{r}
arbuthnot <- read_csv("https://statsmaths.github.io/stat_data/arbuthnot.csv")

```

Here we've used the function `read_csv` to read a file from my website. We
will later in the semester see how to read in data that we have manually
constructed.

Click on the data in the top right hand pane. This will open an Excel
like view of the dataset. Can you describe what the variable `head_of_state`
most likely means? Looking at the data in the data viewer, what years does
the dataset range over?

The Arbuthnot data set refers to Dr. John Arbuthnot, an 18th century
physician, writer, and mathematician. He gathered the baptism records for
children born in London for every year from 1629 to 1710. He was interested
in studying what we would now call the **secondary sex ratio**, the ratio of
males to females in a population at birth. This would later be a major element
of study of Ronald Fisher, one of the most well-known, early pioneering
statisticians.

Draw a scatter plot representing the number of boys baptised (y-axis)
as a function of the year (x-axis).

```{r}

```

Modify the previous plot by coloring the data points as a function of
who was the head of state.

```{r}

```

Modify the previous plot by changing the size relative to the total number of
births that year.

```{r}

```

Modify the previous plot to now make the sizes all equal to 2.

```{r}

```

Finally, add a line connecting the points in the prior plot, but do not color
the line with the heads of state.

```{r}

```

Construct a histogram of the number of the boy_to_girl_ratio variable.
Change the default number of bins (30) to another number. Play around with
the option until you find a plot that you prefer. Note: You may need to
look at the geom_histogram help page.

```{r}

```

Build a plot of the number of girls born in each year (x-axis) and the
number of boys born in each year (y-axis). However, instead of points, place
a text label with `geom_text` showing the year.

```{r}

```

Add a smoothing curve to the prior plot using `geom_smooth`.


```{r}

```

Draw a scatter plot of boys per year (year on the x-axis) but color all
of the points in "olivedrab".

```{r}

```

Now, add the girls birth data to the previous plot but color those
points in salmon (Note: this might take some out of the box thinking, but
requires only tools you've seen today).

```{r}

```

The prior plot's y-axis no longer makes sense (well, probably, depending
on you solved the last question). Change it to something more accurate and
remove the x-axis label entirely as it should be self-explanatory.

```{r}

```

Make an additional plot with the arbuthnot data using geometries that we
have not used yet in class.

```{r}

```








