---
title: "AHA2019 -- Setup"
output: html_notebook
---

## Testing

To start, let's just make sure R is running okay on your computer while
explaining the basic mechanism for using RMarkdown files. Below is a **code
chunk**. Click the green run button to execute the code. The result should
appear directly below.

```{r}
1 + 1
```

You can, and will, edit code chunks with your own R code. Use the chunk below
to calculate the sum of 1 and 2 and execute the code.

```{r}

```
## Further set-up

### Packages

The final step is to download all of the R packages that we will
need for the semester. It is generally easier to do these all at
once rather than as we go along.

To install the packages required for the workshop, run the following lines
of code in the console. There may be a warning about one or two
packages not being available. Note that this may take 5-10 minutes
to finish; on slower connections or older computers, it may take even
longer. If you run into any problems, please let me know!

```{r, eval = FALSE}
pkgs <- c("dplyr", "ggplot2", "stringr", "devtools", "viridis", "plotly",
          "readr")

install.packages(pkgs,
                 repos = "https://cloud.r-project.org",
                 type = "binary",
                 dependencies = TRUE)
```

Now, you will also need install the `smodels` package. We have written
this package for our own courses, and you'll need to install it in a slightly
different way.

```{r, eval = FALSE}
devtools::install_github("statsmaths/smodels")
```

### Defaults

RStudio will work fine for you today with just the packages above. We also
suggest making the following changes as they greatly help when using R on your
own in the future.

- In the RStudio menu click on `Tools > Global Options...`
- Look for the first drop-down: `Save the workspace to .RData on exit`
- Change this first drop-down to `Never`
- All of the check-boxes above this dropdown should be unchecked.


